Exploring dimensions of biodiversity in Japanese ferns

### 2020-08-20 ms/manuscript.Rmd
Update MS

# CANAPE
canape_cols <-
  c(
    "neo" = "#e31a1c", 
    "paleo" = "#1f78b4",
    "mixed" = "#6a51a3",
    "super" = "#4a1486",
    "not significant" = "#ffffcc"
  )
```

@@

```{r bioregions, fig.width = 7, fig.height = 5}
# Taxonomic bioregions
a <- ggplot() +
  geom_sf(data = japan, fill = "grey90", color = "black", lwd = 0.25) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = taxonomic_cluster), color = "transparent", alpha = 0.8) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**A** Taxonomic</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Cluster") +
  scale_fill_carto_d(type = "qualitative", palette = "Bold") +
  # scale_fill_brewer(type = "qual") +
  map_theme()

# Phylogenetic bioregions
b <- ggplot() +
  geom_sf(data = japan, fill = "grey90", color = "black", lwd = 0.25) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = phylo_cluster), color = "transparent", alpha = 0.8) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**B** Phylogenetic</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Cluster") +
  scale_fill_carto_d(type = "qualitative", palette = "Bold") +
  map_theme() +
  theme(
    axis.text.y = element_blank()
  )

>>>>

# CANAPE
canape_cols <-
  c(
    "neo" = "#e31a1c", 
    "paleo" = "#1f78b4",
    "mixed" = "#6a51a3",
    "super" = "#4a1486",
    "not significant" = "#ffffcc"
  )

# Bioregions
bioregion_cols <- rcartocolor::carto_pal(9, "Bold")[1:8] %>%
  set_names(1:8)
```

@@

```{r bioregions, fig.width = 7, fig.height = 5}
# Taxonomic bioregions
a <- ggplot() +
  geom_sf(data = japan, fill = "grey90", color = "black", lwd = 0.25) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = taxonomic_cluster), color = "transparent", alpha = 0.8) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**A** Taxonomic</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Cluster") +
  scale_fill_manual(values = bioregion_cols) +
  map_theme()

# Phylogenetic bioregions
b <- ggplot() +
  geom_sf(data = japan, fill = "grey90", color = "black", lwd = 0.25) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = phylo_cluster), color = "transparent", alpha = 0.8) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**B** Phylogenetic</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Cluster") +
  scale_fill_manual(values = bioregion_cols) +
  map_theme() +
  theme(
    axis.text.y = element_blank()
  )
